Trajipaq_sentiment_an

### 2023-08-12 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_an.Rmd
again

```{r}
stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  reg_WGI_can_arrival_long,
  reg_WGI_can_arrival_long_ctrl,
  title = "Results", 
  align = TRUE, 
  type = "text"
)

>>>>

```{r}
stargazer(
  reg_WGI_can_2021_long,
  reg_WGI_can_2021_long_ctrl,
  reg_WGI_can_arrival_long,
  title = "Results", 
  align = TRUE, 
  type = "text"
)
